---
title: "DDL and Setup Scripts"
subtitle: "Data warehouse DDL, permissions, and dimension table creation"
toc: true
number-sections: true
format:
  html:
    embed-resources: true
execute:
  eval: false
---

# Data Warehouse DDL

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/DW RedShift - DDL.sql"))
cat("```\n")
```

# Permissions

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/00_permissions.sql"))
cat("```\n")
```

# Dimension: County

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/dim_county.sql"))
cat("```\n")
```

# Dimension: State

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/dim_state.sql"))
cat("```\n")
```

# Dimension: CIP

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/dim_cip.sql"))
cat("```\n")
```

# Dimension: Year/Quarter

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/dim_year_quarter.sql"))
cat("```\n")
```

# Dimension: Program

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/dim_program.sql"))
cat("```\n")
```

# Dimension: Person

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/dim_person.sql"))
cat("```\n")
```

# Dimension: Intake Characteristics

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/dim_intake_characteristics.sql"))
cat("```\n")
```
