---
title: "FACT: Person Outcome"
subtitle: "Scripts for loading FACT Person Outcome tables"
toc: true
number-sections: true
format:
  html:
    embed-resources: true
execute:
  eval: false
---

# Load — JOINT PIRL

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/FACT Person Outcome/DW RedShift - Load FACT Person Outcome - JOINT PIRL.sql"))
cat("```\n")
```

# Load — PIRL Adult

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/FACT Person Outcome/DW RedShift - Load FACT Person Outcome - PIRL - Adult.sql"))
cat("```\n")
```

# Load — PIRL Adult Education

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/FACT Person Outcome/DW RedShift - Load FACT Person Outcome - PIRL - Adult Education.sql"))
cat("```\n")
```

# Load — PIRL Dislocated Worker

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/FACT Person Outcome/DW RedShift - Load FACT Person Outcome - PIRL - Dislocated Worker.sql"))
cat("```\n")
```

# Load — PIRL Job Corps

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/FACT Person Outcome/DW RedShift - Load FACT Person Outcome - PIRL - Job Corps.sql"))
cat("```\n")
```

# Load — PIRL Vocational Rehab

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/FACT Person Outcome/DW RedShift - Load FACT Person Outcome - PIRL - Vocational Rehab.sql"))
cat("```\n")
```

# Load — PIRL Wagner-Peyser

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/FACT Person Outcome/DW RedShift - Load FACT Person Outcome - PIRL - Wagner Peyser.sql"))
cat("```\n")
```

# Load — PIRL Youth

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/FACT Person Outcome/DW RedShift - Load FACT Person Outcome - PIRL - Youth.sql"))
cat("```\n")
```

# Load — PIRL Youth Build

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/FACT Person Outcome/DW RedShift - Load FACT Person Outcome - PIRL - Youth Build.sql"))
cat("```\n")
```
