---
title: "FACT: Quarterly Program Enrollment"
subtitle: "Scripts for loading FACT Person Quarterly Program Enrollment tables"
toc: true
number-sections: true
format:
  html:
    embed-resources: true
execute:
  eval: false
---

# Fact Quarterly Program Enrollment (Base)

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/01_fact_quarterly_program_enrollment.sql"))
cat("```\n")
```

# Load FACT Person Quarterly Program Enrollment — JOINT PIRL

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/FACT Person Quarterly Program Enrollment/DW RedShift - Load FACT Person Quarterly Program Enrollment - JOINT PIRL.sql"))
cat("```\n")
```

# Load FACT Person Quarterly Program Enrollment — PIRL

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/FACT Person Quarterly Program Enrollment/DW RedShift - Load FACT Person Quarterly Program Enrollment - PIRL.sql"))
cat("```\n")
```

# Load FACT Person Quarterly Program Enrollment — SNAP

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/FACT Person Quarterly Program Enrollment/DW RedShift - Load FACT Person Quarterly Program Enrollment - SNAP.sql"))
cat("```\n")
```

# Load FACT Person Quarterly Program Enrollment — TANF

```{r echo=FALSE, results='asis'}
cat("```sql\n")
writeLines(readLines("data model scripts/FACT Person Quarterly Program Enrollment/DW RedShift - Load FACT Person Quarterly Program Enrollment - TANF.sql"))
cat("```\n")
```
