---
title: "MDRC- webinar export"
format: html
---
This is an export for State IMPACT
These are summaries of several regression analyses.
Each analysis has the count of unique SSN's used provided.



```{r}
library(tidyverse)
library(ColeridgeInitiative)
library(emmeans)
```

# Data
```{r}
con <- adrf_redshift("training")

library(dbplyr)

dat <- con %>% 
  tbl(in_schema(schema = "tr_state_impact_ada_training",
                table = "nb_analysis_frame")) %>% collect()

```

# regression 1
## Count documentation
```{r}
counts <- dat %>%
  mutate(na_wage_q37 = ifelse(is.na(wages_q37)==T, 0,1),
         na_prior_wage = ifelse(is.na(scale_prior_wages)==T,0,1),
         na_prior_work = ifelse(is.na(quarters_active_prior_2yr)==T,0,1))%>% 
  select(person_key, gender, age_cat, edu_cat,wp_enroll, na_wage_q37, na_prior_wage, na_prior_work) %>%
  mutate(across(c(gender, age_cat, edu_cat, wp_enroll,na_wage_q37, na_prior_wage, na_prior_work), as.character)) %>%
  pivot_longer(
    cols = c( gender, age_cat, edu_cat,wp_enroll,na_wage_q37, na_prior_wage, na_prior_work),
    names_to = "variable",
    values_to = "category"
  ) %>%
  group_by(variable, category) %>%
  summarise(
    n_unique_ssn = n_distinct(person_key),
    .groups = "drop"
  ) %>%
  collect()
  

#counts
```


## Regression output 
```{r}
reg1 <- lm( wages_q37 ~ gender +  age_cat + edu_cat + wp_enroll + scale_prior_wages +quarters_active_prior_2yr , data=dat )

reg1 %>% broom::tidy()

emmeans(reg1, ~age_cat + gender + wp_enroll)
```


## logistic regression output
```{r}
logreg1<- glm( wp_enroll ~ age_cat + gender + edu_cat + scale_prior_wages +quarters_active_prior_2yr , data = dat, family = binomial)

logreg1 %>% broom::tidy()

emmeans(logreg1, ~age_cat +scale_prior_wages ,
        at = list("scale_prior_wages" = c(0, 1)),
         type = "response")
```

# Propensity score analysis

## initial output - less robust

```{r}
library(MatchIt)
library(cobalt)
m <- matchit(wp_enroll ~ gender+ age_cat + edu_cat + eth_recode + scale_prior_wages + scale_prior_year_wage + quarters_active_prior_2yr ,
             data   = dat)
m0 <- summary(m)
m0$sum.matched
#m0

love.plot(m, abs = T) +
  geom_vline(xintercept = 0.1, lty = 2)  
```

## try 2 - more robust

```{r}
match2<- matchit(wp_enroll ~gender+ age_cat +edu_cat+ eth_recode+ scale_prior_wages + scale_prior_year_wage +quarters_active_prior_2yr ,
             data   = dat,         
             caliper = .05)

love.plot(match2, abs=T) + geom_vline(xintercept = 0.1, lty = 2)
```

## Try 3 - most robust

```{r}
m_nn2 <- matchit(wp_enroll ~gender+ age_cat +edu_cat+ eth_recode+ scale_prior_wages + scale_prior_year_wage +quarters_active_prior_2yr ,
             data   = dat,
             exact    = ~ prior_wage_bin ,
             caliper  = 0.05,
             ratio = 2)

m0_nn2<-summary(m_nn2)

m0_nn2$sum.matched

love.plot(m_nn2, abs =T) + geom_vline(xintercept = 0.1, lty = 2)

```



```{r}

matched <- match.data(m_nn2)


library(halfmoon)
ggplot(
  matched,
  aes(distance, fill = factor(wp_enroll))
) +
  geom_mirror_histogram(bins = 50) +
  scale_y_continuous(labels = abs) +
  labs(x = "propensity score", fill = "WP - enrolled")
```

## ATT on result 3
```{r}
weighted_treat <- with(matched, weighted.mean(wages_q41[wp_enroll == 1], weights[wp_enroll == 1]))
weighted_control <- with(matched, weighted.mean(wages_q41[wp_enroll == 0], weights[wp_enroll == 0]))
ATT <- weighted_treat - weighted_control
ATT
```


## Basic regression on mathed results for Q41
```{r}

att_mod <- lm(wages_q41 ~ wp_enroll,
       data = matched, 
       weights = weights)

att_mod %>% broom::tidy()
```


# DIff in Diff analysis
```{sql , output.var="data_did"}
select
        ncm.*,
        fpuw.year_quarter_key,
        fpuw.ui_quarterly_wages
from tr_state_impact_ada_training.nb_analysis_matched ncm
left join tr_state_impact_ada_training.fact_person_ui_wage fpuw
    on ncm.person_key = fpuw.person_key
    and (fpuw.year_quarter_key >=27 and fpuw.year_quarter_key <= 39 or fpuw.ui_quarterly_wages is null)
order by ncm.person_key, fpuw.year_quarter_key 
```


```{r}
data_did <- data_did |>
  mutate(
    treat = as.integer(wp_enroll == 1),   # 1 = ever treated, 0 = never
    post  = as.integer(year_quarter_key >= 31), # 1 = quarter 31+ is "after"
    treat_post =treat*post)
```

## Count documentation for DID analysis
```{r}
counts_did <- data_did %>%
  mutate(na_wage = ifelse(is.na(ui_quarterly_wages)==T, 0,1))%>% 
  select(person_key, treat, post, treat_post, na_wage) %>%
  mutate(across(c(treat, post, treat_post,na_wage), as.character)) %>%
  pivot_longer(
    cols = c( treat, post, treat_post,na_wage),
    names_to = "variable",
    values_to = "category"
  ) %>%
  group_by(variable, category) %>%
  summarise(
    n_unique_ssn = n_distinct(person_key),
    .groups = "drop"
  ) %>%
  collect()
  

#counts_did
```


## DID estimates
```{r}
library(fixest) # need to install first

m_twfe <- feols(
  ui_quarterly_wages ~ treat:post | person_key + year_quarter_key,
  cluster ~ person_key,
  data = data_did
)

coef(m_twfe)
 m_twfe$coeftable
```

```{r, eval = FALSE}
plot_data <- data_did %>%
  group_by(treat, year_quarter_key) %>%
  summarize(mean_wages = mean(ui_quarterly_wages, na.rm = TRUE), .groups = "drop")

ggplot(plot_data, aes(x = year_quarter_key, y = mean_wages, color = factor(treat))) +
  geom_line(size = 1.2) +
  geom_vline(xintercept = 31, linetype = "dashed") +
  labs(
    x = "Quarter",
    y = "Average Quarterly Wages",
    color = "Treatment Group",
    title = "Difference-in-Differences Plot of Wages Over Time"
  ) +
  theme_minimal()
```

